\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2023-05-17 doc/regime_changes_bp_rr.tex
Add analysis subsetting to insig pre-trends

% appendix settings
\usepackage[toc,page,header]{appendix}
\renewcommand{\appendixpagename}{\centering Appendices}
\usepackage{chngcntr}
\usepackage{etoolbox}
\usepackage{lipsum}

@@

\setcounter{tocdepth}{1}
\begin{document}
\author{Devin Incerti\thanks{Independent researcher. devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author. Assistant Professor, Department of Political Science, University of Amsterdam.  t.n.incerti@uva.nl.}}
\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions. Authors are listed in alphabetic order, implying equal authorship. Any and all errors are our own.}}}
\date{\today}
\maketitle
\thispagestyle{empty}

@@

@@

@@

\subsection{Time-shifted placebo test}

\begin{figure}[!htb]
\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
\caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
\label{fig:mean-event-day-ar-by-regime-change}
\end{figure}

>>>>

% appendix settings
\usepackage[toc,page,header]{appendix}
\renewcommand{\appendixpagename}{\centering Appendices}
\usepackage{chngcntr}
\usepackage{etoolbox}
\usepackage{lipsum}
\usepackage{etoc}

@@

%\setcounter{tocdepth}{1}
\begin{document}
\author{Devin Incerti\thanks{Independent researcher. devin.incerti@gmail.com} and Trevor Incerti\thanks{Corresponding author. Assistant Professor, Department of Political Science, University of Amsterdam.  t.n.incerti@uva.nl.}}
\title{\textbf{Are regime changes always bad economics? Evidence from daily financial data \thanks{We are grateful to Peter Aronow, Matthew Graham, and Frances Rosenbluth for helpful feedback and suggestions. Authors are listed in alphabetic order, implying equal authorship. Any and all errors are our own.}}}
\date{\today}
\maketitle
\thispagestyle{empty}

@@

\begin{centering}
\LARGE
\textbf{\textit{Supplementary Appendix:}} \\
 \vspace{0.5cm}
\textbf{Are regime changes always bad economics? Evidence from daily financial data} \\

\vspace{0.5cm}

\large
Devin Incerti and Trevor Incerti

\end{centering}

@@

\localtableofcontents
\pagenumbering{arabic}% resets `page` counter to 1
\renewcommand*{\thepage}{A\arabic{page}}

@@

\subsection{Additional robustness tests}

\subsubsection{Abnormal returns for events with insignificant 7-day pre-trends only}

\begin{table}[H]
\caption{Abnormal returns following coups} \label{tab:AR-coups-pre}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-coups-car-pre.txt}
  \hline
\ExpandableInput{../tables/artable-coups-car-mean-pre.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[H]
\caption{Abnormal returns following assassinations} \label{tab:AR-ass-pre}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-ass-car-pre.txt}
  \hline
\ExpandableInput{../tables/artable-ass-car-mean-pre.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\begin{table}[H]
\caption{Abnormal returns following resignations} \label{tab:AR-resignations-pre}
\vspace{-5pt}
\footnotesize
\begin{center}
\begin{threeparttable}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}ld{4}d{4}d{4}d{4}d{4}d{2}}
  \hline
  \hline
\multicolumn{2}{c}{} & \multicolumn{3}{c}{Post-Event CAR} & \multicolumn{2}{c}{Pre-Event CAR} & \multicolumn{1}{c}{\multirow{2}{*}{Days to}}\\
\cmidrule(r){3-5} \cmidrule(r){6-7}
\multicolumn{1}{c}{Country} & \multicolumn{1}{c}{Event Date} & \multicolumn{1}{c}{(0,0)} & \multicolumn{1}{c}{(0,6)} & \multicolumn{1}{c}{(0,19)} & \multicolumn{1}{c}{(-1,-7)} & \multicolumn{1}{c}{(-1,-20)} & \multicolumn{1}{c}{rebound}\\
  \hline
\ExpandableInput{../tables/artable-res-car-pre.txt}
  \hline
\ExpandableInput{../tables/artable-res-car-mean-pre.txt}
   \hline
   \hline
\end{tabular*}
\scriptsize
Notes: Standard errors are in parentheses. ``Days to rebound'' is the number of trading days following a negative stock return for the national stock index to return to pre-event level (it is calculated if the price decreases on the event day, not if the event day abnormal return is negative). Returns are inflation adjusted. 
\end{threeparttable}
\end{center}
\end{table}

\subsubsection{Time-shifted placebo test}

\begin{figure}[H]
\includegraphics{../figs/mean-ar-by-regime-change-type-placebo.pdf}
\caption{Time-shifted placebo sensitivity analysis of mean event day abnormal return by type of regime change}
\label{fig:mean-event-day-ar-by-regime-change}
\end{figure}
